Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-05-15 minimax.tex
Table 3
Slight rewording Fig 2

\paragraph{Evaluation of Pessimistic Strategy}
\label{sec:lowRegret}
Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
Table 2, first five columns, contain the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a \scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs. It is interesting to note that about twenty or thirty questions per agent on average suffice to reach a low regret in those instances. We find also noteworthy that the Pessimistic strategy chooses to ask zero questions to the chair but still achieves low regret, in most of those instances.

@@

	\begin{minipage}{\textwidth}
		\centering
		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
		\label{tab:twoP500}
		\scalebox{0.85}{
		\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
			\toprule
			{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule		
			0	&0.78&	0.38&	0.78&	0.38\\
			15	&0.58&	0.3	&   0.63&   0.26\\
			30	&0.29&  0.31&	0.4&    0.52\\
			50	&0.0&	0.0&	0.0&	0.0\\
			100	&0.21&	0.36&	0.07&	0.12\\
			200	&2.84&	1.52&	1.72&	1.79\\
			300	&6.02&	2.28&	6.79&	0.81\\
			400	&10.95&	0.74&	12.8&	0.92\\
			500	&20.0&	0.0&	20.0&	0.0\\

>>>>

\paragraph{Evaluation of Pessimistic Strategy}
\label{sec:lowRegret}
Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first.
\cref{tab:questions}, first five columns, contains the result: it displays, for each dataset, the number of questions asked to the chair ($q_{c \scriptscriptstyle{\MMR} ≤ n/10}$), and the quartiles of the number of questions asked to the agents ($q_{a \scriptscriptstyle{\MMR} ≤ n/10}$), averaged over $20$ runs. It is interesting to note that about twenty or thirty questions per agent on average suffice to reach a low regret in those instances. We find also noteworthy that the Pessimistic strategy chooses to ask zero questions to the chair but still achieves low regret, in most of those instances.

@@

	\begin{minipage}{\textwidth}
		\centering
		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
		\label{tab:twoP500}
		\scalebox{0.85}{
		\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
			\toprule
			{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule

			0	&	0.62	&	0.52	&	0.62	&	0.52	\\
			15	&	0.515	&	0.48	&	0.54	&	0.46	\\
			30	&	0.345	&	0.47	&	0.325	&	0.425	\\
			50	&	0.045	&	0.09	&	0.03	&	0.065	\\
			100	&	0.14	&	0.23	&	0.075	&	0.135	\\
			200	&	2.305	&	1.36	&	2.145	&	1.845	\\
			300	&	5.15	&	2.38	&	6.83	&	0.625	\\
			400	&	10.905	&	0.89	&	12.245	&	0.99	\\
			500	&	20.0	&	0.0	&	20.0	&	0.0	\\
